Generating Simulated Data

### 2021-03-17 docs/SimData.Rmd
outline binwidth function

Species specific bin width definitions are an input into the model, with more refined (smaller) bin sizes during rapid growth phases. *Consider a function to do this using species max size and the desired number of bins for more consistency and to easily change Nsizebins.*

@@

#multiple surveys named in list object, use as filename
for(s in names(len_comp_data)){
  #arrange into wide format: year, Species1, Species2 ... and write csv
  svlen <- len_comp_data[[s]][[1]] %>%
    #calc_timestep2time(d.name, ., run.prm.file) %>% #this gives an arbitrary start year of 1970
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, year, atoutput) %>%
    tidyr::spread(species, atoutput) %>%
    write_csv(paste0(o.name,"observation_lengths_NOBA_",s,".csv"))
}

>>>>

Species specific bin width definitions are an input into the model, with more refined (smaller) bin sizes during rapid growth phases.

*Consider a function to do this using species max size, the vonB k and the desired number of bins for more consistency and to easily change Nsizebins.*
```{r lbinfunction, eval=FALSE}
# see e.g., https://www.sciencedirect.com/science/article/abs/pii/S0165783619303297
# estimated optimal bin size for VBGF estimation is 0.23 x Lmax ^0.6

binwidths <- function(Lmax, vonBk, Nsizebins){
  #optimal bin size is lower end
  binopt <- 0.23*Lmax^0.6
  #vonBk tells you how many fine bins for fast growth

  #aggregate bins in multiples of optimal for bigger fish/slower growth to get Nsizebins

}

@@

#multiple surveys named in list object, use as filename
for(s in names(len_comp_data)){
  #arrange into wide format: year, Species1, Species2 ... and write csv
  svlen <- len_comp_data[[s]][[1]] %>%
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, agecl, year, upper.bins, atoutput) %>%

    tidyr::spread(species, atoutput) %>%
    write_csv(paste0(o.name,"observation_lengths_NOBA_",s,".csv"))
}
